Staged Abstract Interpreters

### 2019-06-29 paper/10_intro.tex
misc

\iffalse
  Revision: 
  also motivate from the perspective that ADI is slow,
  analyze the reason: 1) interpretive overhead, 2) the use of monadic layers,
  3) the intrinsic complexity of abs int of HO language (ie CFA particularly).
  Then introduce the abstraction without regret.
  contribution: derive staged monad transformers.
\fi

>>>>

\iffalse
  Revision: 
  source of overhead: 1) interpreration, dispatch, recursion.
  2) modern ai uses effect systems to construcut abs interp, in a purely functional way.
  which has certain benefits, but introduce additional abstraction layers may lead to 
  performance overhead. Such as MAAM, ADI, Semantic

  also motivate from the perspective that ADI is slow,
  analyze the reason: 1) interpretive overhead, 2) the use of monadic layers,
  3) the intrinsic complexity of abs int of HO language (ie CFA particularly).
  Then introduce the abstraction without regret.
  contribution: derive staged monad transformers.
\fi
